This R Markdown file was used for the creation and analysis of our age-of-acquisition (AoA) norms.
It includes:
  - investigation for raw data cleaning 
  - final data cleaning pipeline
  - creation of AoA group estimates
  - analysis of AoA group estimates (including internal + external reliability)


```{r setup}
library(tibble)
library(readr)
library(readxl)
library(readODS)
library(dplyr)
library(magrittr)
library(ggplot2)
library(RColorBrewer)
library(cowplot)
library(stringr)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r define-custom-functions}
source('helper_functions.R', local = knitr::knit_global())
```

```{r load-data}
# LOAD DATA WITH ADDITIONAL FREQUENCY + OTHER CORPORA INFO
aoa_info <- load_raw_data()

# load item information
# get item numbers used as per-participant control items (repeated items)
repeated_a <- read_csv("../../study_setup/data/items_lists/list_A_repeated.csv", col_names="item_number")
repeated_b <- read_csv("../../study_setup/data/items_lists/list_B_repeated.csv", col_names="item_number")
repeated_c <- read_csv("../../study_setup/data/items_lists/list_C_repeated.csv", col_names="item_number")
# turn tibble into list
repeated_items <- c(repeated_a$item_number, repeated_b$item_number, repeated_c$item_number)
# get item numbers used as global control items (shared items)
shared_items <- read_csv("../../study_setup/data/items_lists/control_items.csv", col_names="item_number")
shared_items <- shared_items$item_number
```

```{r participant-overview}
# GET PARTICIPANT SUMMARIES
# limit to one entry per participant
participant_df <- aoa_info[!duplicated(aoa_info$ID),] %>% 
  select(c(ID, platform, list, gender, age, country, education, L1, monoling, sight, children, child_age))

print("Number of participants:")
length(participant_df$ID)
print("Mean age:")
mean(participant_df$age)

# summaries for all relevant columns
participant_df %>% 
    count(platform)
participant_df %>% 
  count(list)
participant_df %>% 
    count(gender)
participant_df %>% 
    count(age)
participant_df %>% 
    count(education)
participant_df %>% 
    count(sight)
participant_df %>% 
    count(children)
participant_df %>% 
    count(child_age)
```

# Database cleaning: Preparations
For full transparency, we include our initial data investigations that informed our final data cleaning pipeline.
The full pipeline is presented neatly in the next section.

```{r exclude-disqualified-participant}
# remove participant who disqualified
aoa_info <- aoa_info %>% 
  filter(ID != 457)
```

```{r check-high-estimates, eval=FALSE}
# check: are high estimates well founded?
aoa_info %>% 
  # !is.na(item_number) excludes familiarisation items (that don't have an item number from the MultiPic corpus)
  filter(!is.na(item_number) & estimate > 20)
```
We argue that all of these ratings are either clear typos or generally very unlikely.

```{r preparations-for-excluding-participants}
# REMOVE ITEMS THAT ARE TYPOS
aoa_info <- aoa_info %>% 
  filter(!is.na(item_number) & !estimate > 20)

# EXCLUDING PARTICIPANTS: Calculate correlations
### KUPERMAN PROCEDURE
kup_procedure <- kuperman_correlations(aoa_info)

### BIRCHENOUGH PROCEDURE
birch_procedure <- birchenough_correlations(aoa_info)

# remove participants that weren't intrinsically consistent enough
within_participant_corrs <- within_participant_corelations(aoa_info)
```


```{r visualise-AoA-distribution-in-Birchenough-and-in-shared-items-(aka-control-items)}
# find out AoA distribution in Birchenough and in shared items
birchenough_norms <- read_birchenough()
birchenough_aoa_bins <- birchenough_norms %>% 
  select(NAME1, `B: AoA mean`) %>% 
  mutate(aoa_bin_threshold = cut(birchenough_norms$`B: AoA mean`, breaks = 10)) %>% 
  mutate(aoa_bin = as.factor(cut(birchenough_norms$`B: AoA mean`, breaks = 10, labels = FALSE)))

# Birchenough AoA distribution plot
birchenough_aoa_dist <- birchenough_aoa_bins %>% 
  ggplot(aes(x=`B: AoA mean`, fill = aoa_bin)) +
  geom_histogram() +
  scale_fill_brewer(palette= "Paired") +
  labs(fill= "AoA bin") +
  theme_minimal()

# shared items AoA distribution plot
kuperman_procedure_shared <- aoa_info[aoa_info$item_number %in% shared_items & !is.na(aoa_info$`B: AoA mean`),]
controlitems_aoa_dist <- kuperman_procedure_shared[1:19,] %>% 
  left_join(select(birchenough_aoa_bins, -`B: AoA mean`), by=join_by(item==NAME1)) %>% 
  ggplot(aes(x=`B: AoA mean`, fill = aoa_bin)) +
  geom_histogram() +
  scale_fill_brewer(palette= "Paired") +
  labs(fill= "AoA bin") +
  theme_minimal()

# display plots next to each other
aoa_distributions_birchenough <- plot_grid(birchenough_aoa_dist, controlitems_aoa_dist, labels= "AUTO", align = "h", rel_widths = c(1.5,1))
# save_plot("../figures/aoa_distribution_control_items.pdf", aoa_distributions_birchenough, ncol=2)
aoa_distributions_birchenough
```

```{r plot-preliminary-group-estimates}
# AoA distribution of control words according to preliminary group mean estimates
prelim_aoa_estimates <- get_estimates_overview(aoa_info, all=FALSE)
prelim_aoa_estimates %>% 
  mutate(control_word = if_else(item_number %in% shared_items, "yes", "no")) %>% 
  ggplot(aes(x= estimate_mean, fill = control_word)) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(prelim_aoa_estimates$estimate_mean)), linetype=2) +
  scale_fill_brewer(palette= "Paired") +
  labs(title = "Distribution of preliminary AoA group estimates",
       caption = "Mean AoA estimates before further participants were excluded (based on Kuperman (2012)\nor Birchenough (2017) procedure). Dashed line denotes the overall mean of AoA estimates.") +
  theme_minimal()
```
```{r}
mean(prelim_aoa_estimates$estimate_mean)
```

```{r plot-control-items-correlation-Kuperman}
# Kuperman exclusion
# distribution of correlations + which participants would be removed
plot_corr_distribution(kup_procedure$corr_df, kup_procedure$weak_corr_ids, 
                       title = "Correlations of control items: Kuperman (2012) method",
                       caption = "Distribution of the correlations of control item ratings to AoA ratings in Birchenough et al. (2017).\n Exclusion of participants with correlation < 0.4. Dashed line denotes the group mean of correlations.")
```
```{r}
mean(kup_procedure$corr_df$corr)
```

```{r view-Kuperman-correlations, eval=FALSE}
kup_procedure$corr_df %>% 
  filter(corr < 0.45) %>%
  arrange(corr) # sort ascending
```
The subjects close to the proposed threshold of 0.4 (339, 328, 301) seem to be part of the normal distribution.

```{r save-plot-control-items-correlation-Kuperman, eval=FALSE}
# save_corr_distribution_plot(kup_procedure$corr_df, kup_procedure$weak_corr_ids, 
#                             save_path = "../figures/before_cleaning/corr-control-items_Kuperman-method.pdf")
```

```{r plot-control-items-correlation-Birchenough}
# Birchenough exclusion
# distribution of correlations + which participants would be removed
plot_corr_distribution(birch_procedure$corr_df, birch_procedure$weak_corr_ids, 
                       title = "Correlations of control items: Birchenough (2017) method",
                       caption = "Distribution of the correlations of control item ratings to item group mean ratings.\n Exclusion of participants with correlation < 0.4. Dashed line denotes the group mean of correlations.")
```
```{r}
mean(birch_procedure$corr_df$corr)
```

```{r view-Birchenough-correlations, eval=FALSE}
birch_procedure$corr_df %>% 
  filter(corr < 0.45) %>%
  arrange(corr) # sort ascending
```
Again, the subjects close to the proposed threshold of 0.4 (301) seem to be part of the normal distribution.

```{r save-plot-control-items-correlation-Birchenough, eval=FALSE}
# save_corr_distribution_plot(birch_procedure$corr_df, birch_procedure$weak_corr_ids, 
#                             save_path = "../figures/before_cleaning/corr-control-items_Birchenough-method.pdf")
```

```{r}
# how many control items don't have an AoA estimate in Birchenough et al.?
missing_shared_estimates <- sum(is.na(aoa_info[aoa_info$ID == 246 & aoa_info$item_number %in% shared_items,]$"B: AoA mean"))
missing_shared_estimates
```

```{r}
# number of participants excluded according to Kuperman (2012) procedure
print("r < 0.4:")
length(kup_procedure$weak_corr_ids) 
print("Outliers far from main distribution (r < 0.3):")
length(kup_procedure$corr_df[kup_procedure$corr_df$corr < 0.3,]$ID)
```

```{r}
# number of participants excluded according to Birchenough (2017) procedure
print("r < 0.4:")
length(birch_procedure$weak_corr_ids) 
print("Outliers far from main distribution (r < 0.3):")
length(birch_procedure$corr_df[birch_procedure$corr_df$corr < 0.3,]$ID) 
```

```{r plot-internal-reliability}
plot_corr_distribution(within_participant_corrs$corr_df, within_participant_corrs$weak_corr_ids, 
                       title = "Internal reliability of participants",
                       caption = "Distribution of the correlations of repeated item ratings within each participant.\n Exclusion of participants with correlation < 0.4. Dashed line denotes the group mean of correlations.")
```
```{r}
mean(within_participant_corrs$corr_df$corr)
```

```{r, eval=FALSE}
within_participant_corrs$corr_df %>% 
  filter(corr < 0.45) %>%
  arrange(corr) # sort ascending
```

```{r plot-internal-reliability, eval=FALSE}
# save_corr_distribution_plot(within_participant_corrs$corr_df, within_participant_corrs$weak_corr_ids,
#                             save_path = "../figures/before_cleaning/corr-internal-reliability_repeated-items.pdf")
```

```{r}
# number of participants excluded because of internal unreliability
print("r < 0.4:")
length(within_participant_corrs$weak_corr_ids)
print("Outliers far from main distribution (r < 0.3):")
length(within_participant_corrs$corr_df[within_participant_corrs$corr_df$corr < 0.3,]$ID) 
```

```{r}
# if all exclusion parameters combined, how many participants actually excluded?
print("r < 0.4:")
length(unique(c(birch_procedure$weak_corr_ids, kup_procedure$weak_corr_ids, within_participant_corrs$weak_corr_ids)))
print("Outliers far from main distribution (r < 0.3):")
length(unique(c(birch_procedure$corr_df[birch_procedure$corr_df$corr < 0.3,]$ID, 
                kup_procedure$corr_df[kup_procedure$corr_df$corr < 0.3,]$ID, 
                within_participant_corrs$corr_df[within_participant_corrs$corr_df$corr < 0.3,]$ID)))
```

# Full cleaning pipeline

```{r full-cleaning-pipeline}
# EXCLUDING PARTICIPANTS + OUTLIERS
# load raw data again to perform the whole cleaning in one cell
aoa_info <- load_raw_data()
# load item information
# get item numbers used as per-participant control items (repeated items)
repeated_a <- read_csv("../../study_setup/data/items_lists/list_A_repeated.csv", col_names="item_number")
repeated_b <- read_csv("../../study_setup/data/items_lists/list_B_repeated.csv", col_names="item_number")
repeated_c <- read_csv("../../study_setup/data/items_lists/list_C_repeated.csv", col_names="item_number")
# turn tibble into list
repeated_items <- c(repeated_a$item_number, repeated_b$item_number, repeated_c$item_number)
# get item numbers used as global control items (shared items)
shared_items <- read_csv("../../study_setup/data/items_lists/control_items.csv", col_names="item_number")
shared_items <- shared_items$item_number

# manual exclusion
aoa_info <- aoa_info %>%
  # remove participant who disqualified
  filter(ID != 457) %>%
  # remove typos
  filter(!is.na(item_number) & !estimate > 20) 

# Calculate correlations
kup_procedure <- kuperman_correlations(aoa_info)
birch_procedure <- birchenough_correlations(aoa_info)
within_participant_corrs <- within_participant_corelations(aoa_info)

# automatic exclusion
aoa_info <- aoa_info %>%
  # Kuperman procedure; outliers far from main distribution
  filter(! ID %in% kup_procedure$corr_df[kup_procedure$corr_df$corr < 0.3,]$ID) %>% 
  # Birchenough procedure; outliers far from main distribution
  filter(! ID %in% birch_procedure$corr_df[birch_procedure$corr_df$corr < 0.3,]$ID) %>% 
  # internally unreliable participants
  filter(! ID %in% within_participant_corrs$corr_df[within_participant_corrs$corr_df$corr < 0.3,]$ID)
  
# remove single items that are outliers
prelim_aoa_estimates <- get_estimates_overview(aoa_info, all=FALSE)
aoa_info <- aoa_info %>% 
  filter(!is.na(item_number)) %>% 
  left_join(prelim_aoa_estimates, by=join_by(item_number)) %>%
  mutate(lower_2sd = estimate_mean-2.5*estimate_sd,
         upper_2sd = estimate_mean+2.5*estimate_sd) %>%
  mutate(in_sd_range = between(estimate, lower_2sd, upper_2sd)) %>% 
  # exclude outliers > 2 sd
  filter(in_sd_range == TRUE)
```

# Generation of group estimate means

```{r calculate-group-estimates, include=FALSE}
# GET GROUP ESTIMATES
aoa_estimates <- get_estimates_overview(aoa_info)
# merge mean estimate information with additional information from aoa_info
aoa_estimates <- aoa_estimates %>% 
  left_join(select(aoa_info, c("item", "item_number", "example_sentence", "H_INDEX","VISUAL_COMPLEXITY", "lgSUBTLEX", "B: AoA mean", "B: AoA SD", "B: min", "B: max", "B: AoALikert mean", "B: AoALikert SD", "B: minLikert", "B: maxLikert", "S: AoALikert mean", "S: AoALikert SD")), by=join_by("item_number"), multiple="first")
aoa_estimates <- aoa_estimates %>% 
  relocate(item, .after = item_number)

# save 
# write_excel_csv(aoa_estimates, "../data/aoa_estimates_unique.csv")

# show
aoa_estimates
```



# Data analysis

```{r}
# load saved group mean aoa estimates
aoa_estimates <- read_csv("../data/aoa_estimates_unique.csv")
```

```{r rating-visualisations}
# RATING VISUALISATIONS
num_ratings_participants <- aoa_info %>% count(ID, sort = TRUE) 
num_ratings_participants %>% 
  ggplot(aes(x=ID, y=n)) + 
  geom_point() +
  labs(title = "Number of ratings per participant after preprocessing") +
  xlab("participant ID") +
  ylab("number of ratings") +
  theme_minimal()

num_ratings_words <- aoa_info %>% 
  filter(repetition == 0 & !is.na(item_number) & !item_number %in% shared_items) %>%
  count(item_number, sort = TRUE)  
num_ratings_words %>% 
  ggplot(aes(x=item_number, y=n)) + 
  geom_point() +
  labs(title = "Number of ratings per word after preprocessing") +
  xlab("item number") + 
  ylab("number of ratings") +
  theme_minimal()
```
```{r}
mean(num_ratings_participants$n)
mean(num_ratings_words$n)
```

```{r save-rating-visualisations, eval=FALSE}
# rat_per_sub <-  aoa_info %>%
#                   count(ID, sort = TRUE) %>%
#                   ggplot(aes(x=ID, y=n)) +
#                   xlab("participant ID") +
#                   ylab("number of ratings") +
#                   geom_point() +
#                   theme_minimal()
# rat_per_word <- aoa_info %>%
#                   filter(repetition == 0 & !is.na(item_number) & !item_number %in% shared_items) %>%
#                   count(item_number, sort = TRUE) %>%
#                   ggplot(aes(x=item_number, y=n)) +
#                   xlab("item number") +
#                   ylab("number of ratings") +
#                   geom_point() +
#                   theme_minimal()
# save_plot("../figures/after_cleaning/num_ratings_per_participant.pdf", rat_per_sub)
# save_plot("../figures/after_cleaning/num_ratings_per_word.pdf", rat_per_word)
```


```{r range-comparison-birchenough}
# how do our estimates fit into Birchenough's bin ranges? 

# uncomment the lines below if birchenough_aoa_bins has not been calculated before
# birchenough_norms <- read_birchenough()
# birchenough_aoa_bins <- birchenough_norms %>%
#   select(NAME1, `B: AoA mean`) %>%
#   mutate(aoa_bin_threshold = cut(birchenough_norms$`B: AoA mean`, breaks = 10)) %>%
#   mutate(aoa_bin = as.factor(cut(birchenough_norms$`B: AoA mean`, breaks = 10, labels = FALSE)))

birchenough_bin_ranges <- levels(birchenough_aoa_bins$aoa_bin_threshold)
birchenough_bin_low <- as.numeric( sub("\\((.+),.*", "\\1", birchenough_bin_ranges))
birchenough_bin_low <- birchenough_bin_low[-1] # drop first breakpoint
bin_breaks <- c(0, birchenough_bin_low)
aoa_estimates %>%
  mutate(aoa_bin_threshold = cut(aoa_estimates$estimate_mean, breaks = bin_breaks)) %>%
  mutate(aoa_bin = as.factor(cut(aoa_estimates$estimate_mean, breaks = bin_breaks, labels = FALSE))) %>% 
  ggplot(aes(x=estimate_mean, fill = aoa_bin)) +
  geom_histogram() +
  scale_fill_brewer(palette= "Paired") +
  labs(fill= "AoA bin") +
  xlab("AoA estimates") +
  labs(title = "Distribution of MultiPic age-of-acquisition estimates", caption = "Age bins used from the 10-bin calculation of all Birchenough et al. (2017) estimates.") +
  theme_minimal()
```
```{r save-range-comparison-birchenough, eval=FALSE}
# range_plot <- aoa_estimates %>%
#                 mutate(aoa_bin_threshold = cut(aoa_estimates$estimate_mean, breaks = bin_breaks)) %>%
#                 mutate(aoa_bin = as.factor(cut(aoa_estimates$estimate_mean, breaks = bin_breaks, labels = FALSE))) %>%
#                 ggplot(aes(x=estimate_mean, fill = aoa_bin)) +
#                 geom_histogram() +
#                 scale_fill_brewer(palette= "Paired") +
#                 labs(fill= "AoA bin") +
#                 xlab("AoA estimates") +
#                 theme_minimal()
# save_plot("../figures/after_cleaning/aoa_bin_range_comparison_birchenough.pdf", range_plot)
# 
# lightblue <- RColorBrewer::brewer.pal(4, "Paired")[1]
# range_plot_without_comparison <- aoa_estimates %>%
#                 ggplot(aes(x=estimate_mean)) +
#                 geom_histogram(fill = lightblue) +
#                 xlab("AoA estimates") +
#                 theme_minimal()
# save_plot("../figures/after_cleaning/aoa_distribution.pdf", range_plot_without_comparison)
```

```{r distribution-mean-std, eval=FALSE}
mean(aoa_estimates$estimate_mean)
sd(aoa_estimates$estimate_mean)
min(aoa_estimates$estimate_mean)
max(aoa_estimates$estimate_mean)
```

## Internal reliability

```{r calculate-internal-correlation}
# redo internal correlations after database cleaning
# if not done before, run the data preprocessing cell
within_participant_corrs_preprocessed <- within_participant_corelations(aoa_info)

# plot
lightblue <- RColorBrewer::brewer.pal(4, "Paired")[1]
within_participant_corrs_preprocessed$corr_df %>% 
  ggplot(aes(x=corr)) + 
  geom_histogram(bins = 30, fill = lightblue) +
  geom_vline(aes(xintercept = mean(within_participant_corrs_preprocessed$corr_df$corr)), linetype=2) +
  coord_cartesian(xlim = c(0,1)) +
  labs(title = "Internal reliability of participants", caption = "Distribution of the correlations of repeated item ratings within each participant.\n Dashed line denotes the group mean of correlations.") +
  theme_minimal()
```
```{r, eval=FALSE}
mean(within_participant_corrs_preprocessed$corr_df$corr)
```

```{r save-internal-correlation-plot, eval=FALSE}
# lightblue <- RColorBrewer::brewer.pal(4, "Paired")[1]
# corr_plot <- within_participant_corrs_preprocessed$corr_df %>%
#     ggplot(aes(x=corr)) +
#     geom_histogram(bins = 30, fill=lightblue) +
#     geom_vline(aes(xintercept = mean(within_participant_corrs_preprocessed$corr_df$corr)), linetype=2) +
#     coord_cartesian(xlim = c(0,1)) +
#     theme_minimal()
# save_plot("../figures/after_cleaning/corr-internal-reliability_repeated-items.pdf",corr_plot)
```


## External reliability
### German-German
```{r calculate-external-reliability-german}
# BIRCHENOUGH
birchenough_subset <- aoa_estimates %>% 
  # exclude rows that don't have an estimate in Birchenough et al. (2017)
  filter(!is.na(`B: AoA mean`))  
# how many words in common?
birchenough_common_words <- length(birchenough_subset$item_number)
# calculate correlation
birchenough_corr <- cor(birchenough_subset$estimate_mean, birchenough_subset$`B: AoA mean`)

# SCHRÖDER
schröder_subset <- aoa_estimates %>% 
  # exclude rows that don't have an estimate in Schröder et al. (2012)
  filter(!is.na(`S: AoALikert mean`))  
# how many words in common?
schröder_common_words <- length(schröder_subset$item_number)
# Likert - Likert correlation
schröder_corr_likertlikert <- cor(schröder_subset$estimateLikert_mean, schröder_subset$`S: AoALikert mean`)
# mean estimates - Likert correlation
schröder_corr_estimateslikert <- cor(schröder_subset$estimate_mean, schröder_subset$`S: AoALikert mean`)
```

```{r, eval=FALSE}
birchenough_subset
```


```{r visualise-external-reliability-german}
# our estimates vs. Birchenough
birchenough_estimates_plot <- aoa_estimates %>% 
  filter(!is.na(`B: AoA mean`))  %>% 
  ggplot(aes(x=`B: AoA mean`, y=estimate_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", x=3.35, y=9.9, label=paste("cor =",round(birchenough_corr, digits=3)), color="blue") +
  labs(caption = "Mean age-of-acquisition (AoA) ratings of Birchenough et al. (2017; collected on continuous scale)\nplotted against the present mean AoA ratings (collected on continuous scale).") +
  theme_minimal()

# our estimates vs. Schröder
schröder_likertlikert_plot <- aoa_estimates %>% 
  filter(!is.na(`S: AoALikert mean`)) %>%   
  ggplot(aes(x=`S: AoALikert mean`, y=estimateLikert_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", x=1.85, y=5.1, label=paste("cor =",round(schröder_corr_likertlikert, digits=3)), color="blue") +
  labs(caption = "Mean age-of-acquisition (AoA) ratings of Schröder et al. (2012; collected on 7-point Likert scale)\nplotted against the present mean AoA ratings (collected on continuous scale, transformed into 7-point Likert scale).") +
  theme_minimal()

schröder_estimateslikert_plot <- aoa_estimates %>% 
  filter(!is.na(`S: AoALikert mean`)) %>%   
  ggplot(aes(x=`S: AoALikert mean`, y=estimate_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  annotate("text", x=1.8, y=9.9, label=paste("cor =",round(schröder_corr_estimateslikert, digits=3)), color="blue") +
  labs(caption = "Mean age-of-acquisition (AoA) ratings of Schröder et al. (2012; collected on 7-point Likert scale)\nplotted against the present mean AoA ratings (collected on continuous scale).") +
  theme_minimal()

birchenough_estimates_plot
schröder_likertlikert_plot
schröder_estimateslikert_plot
```

```{r save-visualisation-external-reliability-german, eval=FALSE}
# # our estimates vs. Birchenough
# birchenough_estimates_plot <- aoa_estimates %>%
#   filter(!is.na(`B: AoA mean`))  %>%
#   ggplot(aes(x=`B: AoA mean`, y=estimate_mean)) +
#   geom_point() +
#   geom_smooth(method = "lm") +
#   annotate("text", x=3.35, y=9.9, label=paste("cor =",round(birchenough_corr, digits=3)), color="blue") +
#   ylab("estimate mean") +
#   xlab("estimate mean: Birchenough et al. (2017)") +
#   theme_minimal()
# 
# save_plot("../figures/after_cleaning/external_reliability_Birchenough.pdf", birchenough_estimates_plot)
# 
# # our estimates vs. Schröder
# schröder_likertlikert_plot <- aoa_estimates %>%
#   filter(!is.na(`S: AoALikert mean`)) %>%
#   ggplot(aes(x=`S: AoALikert mean`, y=estimateLikert_mean)) +
#   geom_point() +
#   geom_smooth(method = "lm") +
#   annotate("text", x=1.85, y=5.1, label=paste("cor =",round(schröder_corr_likertlikert, digits=3)), color="blue") +
#   ylab("Likert-transformed estimate mean") +
#   xlab("Likert-scale estimate mean: Schröder et al. (2012)") +
#   theme_minimal()
# 
# save_plot("../figures/after_cleaning/external_reliability_Schröder_likertlikert.pdf", schröder_likertlikert_plot)
# 
# schröder_estimateslikert_plot <- aoa_estimates %>%
#   filter(!is.na(`S: AoALikert mean`)) %>%
#   ggplot(aes(x=`S: AoALikert mean`, y=estimate_mean)) +
#   geom_point() +
#   geom_smooth(method = "lm") +
#   annotate("text", x=1.8, y=9.9, label=paste("cor =",round(schröder_corr_estimateslikert, digits=3)), color="blue") +
#   ylab("estimate mean") +
#   xlab("Likert-scale estimate mean: Schröder et al. (2012)") +
#   theme_minimal()
# 
# save_plot("../figures/after_cleaning/external_reliability_Schröder_estimateslikert.pdf", schröder_estimateslikert_plot)
```

```{r show-overlap-and-corr-german, eval=FALSE}
birchenough_common_words
birchenough_corr
schröder_common_words
schröder_corr_likertlikert
schröder_corr_estimateslikert

# how many unique MultiPic items could be covered through combining
# AoA estimates from Birchenough (2017) + Schröder (2012)?
nrow(aoa_estimates[!is.na(aoa_estimates$`B: AoA mean`) | !is.na(aoa_estimates$`S: AoALikert mean`),])
```
### German-English
```{r calculate-external-reliability-english}
# KUPERMAN
# English norms from Kuperman et al. (2012)
kuperman_norms <- read_excel('../../external_resources/norms/Kuperman_2012.xlsx', na=c("#N/A", "NA"))
# get English translation (from MultiPic)
multipic_translations <- read_ods('../../study_setup/data/english_translation.ods') 
# words in Kuperman don't contain any spaces, but our translations do
# therefore, we need to remove spaces
multipic_translations$EN_US <- str_replace_all(multipic_translations$EN_US, " ","")
# merge aoa estimates, translation, and Kuperman estimates
multipic_translations <- multipic_translations %>% 
  select(c(ITEM,EN_US)) %>% 
  left_join(select(kuperman_norms, c(Word,Rating.Mean,Rating.SD)), by=join_by("EN_US"=="Word")) %>% 
  rename(all_of(c("K: AoA mean"="Rating.Mean", "K: AoA SD"="Rating.SD")))
aoa_estimates <- aoa_estimates %>% 
  left_join(multipic_translations, by=join_by("item_number"=="ITEM"))


kuperman_subset <- aoa_estimates %>% 
  # exclude rows that don't have an estimate in Kuperman et al. (2012)
  filter(!is.na(`K: AoA mean`))  
# how many words in common?
kuperman_common_words <- length(kuperman_subset$item_number)
# calculate correlation
kuperman_corr <- cor(kuperman_subset$estimate_mean, kuperman_subset$`K: AoA mean`)
```

```{r visualise-external-reliability-english}
# our estimates vs. Kuperman
kuperman_estimates_plot <- aoa_estimates %>% 
  filter(!is.na(`K: AoA mean`))  %>% 
  ggplot(aes(x=`K: AoA mean`, y=estimate_mean)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(caption = "Mean age-of-acquisition (AoA) ratings of Kuperman et al. (2012; collected on continuous scale)\nplotted against the present mean AoA ratings (collected on continuous scale).") +
  theme_minimal()

kuperman_estimates_plot
```

```{r show-overlap-and-corr-english, eval=FALSE}
kuperman_common_words
kuperman_corr
```

```{r save-visualisation-external-reliability-english, eval=FALSE}
# # our estimates vs. Kuperman
# kuperman_estimates_plot <- aoa_estimates %>%
#   filter(!is.na(`K: AoA mean`))  %>%
#   ggplot(aes(x=`K: AoA mean`, y=estimate_mean)) +
#   geom_point() +
#   geom_smooth(method = "lm") +
#   annotate("text", x=3.65, y=11.5, label=paste("cor =",round(kuperman_corr, digits=3)), color="blue") +
#   ylab("estimate mean") +
#   xlab("estimate mean: Kuperman et al. (2012)") +
#   theme_minimal()
# 
# save_plot("../figures/after_cleaning/external_reliability_Kuperman.pdf", kuperman_estimates_plot)
```

